Cognate beginnings to bilingual lexical growth

### 2023-05-19 manuscript/_appendix/_model-diagnostics.qmd

One way to diagnose the behaviour of MCMC is to inspect whether the different MCMC chains (if more than one) have converged to a similar region of the posterior. The Gelman-Rubin diagnostic [$\hat{R}$ or R-hat @gelman1992inference] provides a measure of chain convergence by comparing the variance within each chain *versus* the variance between each chain. Both are expected to be identical when chains have perfectly converged, so that $\hat{R} = 1$. Values lower than 1.01 are recommended, while values higher than 1.05 indicate that chains might have trouble converging and therefore the estimated parameters must be taken with caution. {apafg-model-rhats-neffs} (A) shows the distribution of $\hat{R}$ values for the coefficients of the fixed effect of our models, which we used for statistical inference. Most values are lower than 1.01, and never higher than 1.05, which provides evidence of successful MCMC convergence.

Another diagnostic of good MCMC converge is the ratio of effective sample size to total sample size ($N_{eff}/N$), which indicates the proportion of samples in the chain that resulted from a non-divergent transition. Values closer to 1 are ideal, as they indicate that all posterior samples from the MCMC were used to estimate the posterior distribution of the parameter. Values larger than 0.1 are recommended. {apafg-model-rhats-neffs} (B) shows the distribution of the effective sample sizes of the coefficients of the fixed effects in our models. Most values are larger than 0.1, although model 0 ($\mathcal{M}_0$) accumulates most effective sample sizes close to 0.1.

```{r apafg-model-rhats-neffs}
#| label: apafg-model-rhats-neffs
#| apa-cap: "Gelman-Rubin (R-hat) convergence diagnostic of the MCMC chains in the Bayesian models."
#| echo: false
#| message: false
#| warning: false
#| fig-height: 6
#| fig-width: 9
#| out-width: 100%
map_df(model_rhats, bind_rows, .id = "model") |> 
    mutate(model = paste0("Model ", str_extract(model, "[0-9]"))) |> 
    pivot_longer(-model, 
                 names_to = ".variable",
                 values_to = ".rhat") |>
    drop_na() |> 
    ggplot(aes(.rhat)) +
    facet_wrap(~model, nrow = 1) +
    geom_vline(xintercept = 1.01, linetype = "dashed") +
    geom_histogram(binwidth = 0.001, colour = "white", fill = "grey60") +
    labs(x = "Gelman Rubin diagnostic (R-hat)",
         y = "MCMC samples",
         title = "Gelman-Rubin (R-hat) diagnostic") +

@@

```{r apafg-model-ppc}
#| label: apafg-model-ppc
#| apa-cap: "Model posterior predictive checks (PPC). Bars indicate the observed proportion of responses to each category (No, Understands, and Understands and Says). Blue dots and error bars represent the mean proportion of responses simulated from the posterior for each category, and its 95\\% interval."
#| eval: true
#| echo: false
#| warning: false
#| message: false
#| fig-width: 6
#| fig-height: 3
#| out-width: 80%
#| out-height: 80%
y_int <- as.integer(as.integer(responses$response))
color_scheme_set(c(rep("grey60", 2), rep("black", 4)))

>>>>

One way to diagnose the behaviour of MCMC is to inspect whether the different MCMC chains (if more than one) have converged to a similar region of the posterior. The Gelman-Rubin diagnostic [$\hat{R}$ or R-hat @gelman1992inference] provides a measure of chain convergence by comparing the variance within each chain *versus* the variance between each chain. Both are expected to be identical when chains have perfectly converged, so that $\hat{R} = 1$. Values lower than 1.01 are recommended, while values higher than 1.05 indicate that chains might have trouble converging and therefore the estimated parameters must be taken with caution. @tbl-rhats-neffs (A) shows the distribution of $\hat{R}$ values for the coefficients of the fixed effect of our models, which we used for statistical inference. Most values are lower than 1.01, and never higher than 1.05, which provides evidence of successful MCMC convergence.

Another diagnostic of good MCMC converge is the ratio of effective sample size to total sample size ($N_{eff}/N$), which indicates the proportion of samples in the chain that resulted from a non-divergent transition. Values closer to 1 are ideal, as they indicate that all posterior samples from the MCMC were used to estimate the posterior distribution of the parameter. Values larger than 0.1 are recommended. @tbl-rhats-neffs (B) shows the distribution of the effective sample sizes of the coefficients of the fixed effects in our models. Most values are larger than 0.1, although model 0 ($\mathcal{M}_0$) accumulates most effective sample sizes close to 0.1.

```{r tbl-rhats-neffs}
#| label: tbl-rhats-neffs
#| tbl-cap: "Gelman-Rubin (R-hat) convergence diagnostic of the MCMC chains in the Bayesian models."
#| echo: false
#| message: false
#| warning: false
#| fig-height: 6
#| fig-width: 9
#| out-width: 100%
map_df(model_rhats, bind_rows, .id = "model") |> 
    mutate(model = paste0("Model ", str_extract(model, "[0-9]"))) |> 
    pivot_longer(-model, 
                 names_to = ".variable",
                 values_to = ".rhat") |>
    drop_na() |> 
    ggplot(aes(.rhat)) +
    facet_wrap(~model, nrow = 1) +
    geom_vline(xintercept = 1.01, linetype = "dashed") +
    geom_histogram(binwidth = 0.001, colour = "white", fill = "grey60") +
    labs(x = "Gelman Rubin diagnostic (R-hat)",
         y = "MCMC samples",
         title = "Gelman-Rubin (R-hat) diagnostic") +

@@

```{r tbl-ppc}
#| label: tbl-ppc
#| tbl-cap: "Model posterior predictive checks (PPC). Bars indicate the observed proportion of responses to each category (No, Understands, and Understands and Says). Blue dots and error bars represent the mean proportion of responses simulated from the posterior for each category, and its 95\\% interval."
#| eval: true
#| echo: false
#| warning: false
#| message: false
#| fig-width: 6
#| fig-height: 3
#| out-width: 80%
#| out-height: 80%
y_int <- as.integer(as.integer(responses$response))
color_scheme_set(c(rep("grey60", 2), rep("black", 4)))

### 2023-05-19 manuscript/_appendix/_syllable-frequency.qmd

```{r items-table}
#| label: tbl-items
#| tbl-cap: Sample of items included in the BVQ questionnaire and their syllabified SAMPA transcriptions in Catalan and Spanish
#| echo: false
#| warning: false
#| message: false
items |> 
    distinct(te, item, language, meaning, xsampa, n_syll) |> 
    left_join(distinct(pool_tmp, te, language, item, label),
              by = join_by(te, item, language)) |> 
    pivot_wider(names_from = language,
                values_from = c(item, label, xsampa, n_syll),
                id_cols = c(te, meaning),
                names_repair = make_clean_names,
                values_fn = first) |> 
    sample_n(15) |> 
    gt() |> 
    cols_hide(c(te, item_catalan, item_spanish)) |> 
    tab_spanner("Catalan", matches("catalan")) |> 
    tab_spanner("Spanish", matches("spanish")) |> 
    cols_label(meaning = "Translation",
               label_catalan = "Item",
               xsampa_catalan = "X-SAMPA",
               n_syll_catalan = "Syllables",
               label_spanish = "Item",
               xsampa_spanish = "X-SAMPA",
               n_syll_spanish = "Syllables") |> 
    tab_style(cell_text(weight = "bold"),
              cells_column_spanners()) |> 
    tab_style(cell_text(style = "italic"),
              cells_column_labels())
```

Most Catalan and Spanish words had two syllables, with Spanish words having three and four syllables more often than Catalan words. Less than 1% of the words included in the analyses presented in the main body of the manuscripts had five syllables. No words had more than five syllables (see {apafg-syl-number}). We extracted lexical frequencies from the English corpora in the CHILDES database. Using the Catalan and Spanish corpora was not possible due to the low number of children and tokens included in the corpora.

```{r apafg-syl-number}
#| label: apafg-syl-number
#| apa-cap: Distribution of the number of syllables in Catalan and Spanish
#| fig-width: 7
#| fig-height: 3
#| echo: false
#| warning: false
#| message: false
pool_tmp |> 
    group_by(language) |> 
    add_count(language, name = "n_lang") |> 
    ungroup() |> 
    count(language, n_lang, n_syll) |> 
    mutate(prop = n/n_lang) |> 
    ggplot(aes(n_syll, n)) +
    facet_wrap(~ language) +
    geom_col(colour = "white", fill = "grey70") +
    geom_text(aes(label = percent(prop)),
              size = 3,
              position = position_nudge(y = 15),
              colour = "black") +
    labs(x = "Number of syllables",
         y = "Number of words",
         fill = "Language") +
    theme(legend.position = "none",
          panel.grid.minor = element_blank(),
          panel.grid.major.x = element_blank())
```

We now present how syllable frequencies were calculated. Every exposure to a word-form also counts as a exposure to each of the syllables that make up such word. Every time a child hears the word *casa* [house], they are exposed to the syllables *ca* and *sa*. Syllables that appear embedded in words with higher lexical frequency will also be more frequent. To compute the relative frequency of each syllable in Catalan and Spanish (i.e., how many times the syllables appears in every million words in Catalan or Spanish speech), we summed the relative lexical frequency in CHILDES of every word that contains such syllable in the corresponding language. {apafg-syl-freq} shows the distribution of frequencies across syllables in Catalan and Spanish. In the log10 scale, syllable frequencies in Catalan and Spanish followed a slightly asymmetric distribution, with most syllables scoring around 1,000 counts per million, and a longer tail to the right of the distribution.

```{r apafg-syl-freq}
#| label: apafg-syl-freq
#| apa-cap: "Distribution of apositional syllable frequencies in Spanish and Catalan"
#| fig-height: 3.5
#| fig-width: 7
#| echo: false
#| warning: false
#| message: false
syll <- items |> 
    left_join(distinct(pool_tmp, te, childes_lemma),
              by = join_by(te)) |> 
    left_join(select(childes, token, freq_lex = freq_million),
              by = c("childes_lemma" = "token")) |> 
    select(language, item, te, meaning, xsampa, lv, freq_lex, syll) |> 
    unnest_longer(syll) |> 
    group_by(language, syll) |> 
    summarise(freq_syll = sum(freq_lex),
              .groups = "drop") |> 
    arrange(language, desc(freq_syll))

@@

{apafg-top-syll-freq} shows the top twenty most frequent syllables in Spanish. In both languages, most of the most frequent syllables followed a consonant-vowel (CV) structured. In Catalan, the most common nucleus in the most frequent syllables was /\textschwa/ (most likely due to vowel reduction in unstressed syllables), followed by /u/. In Spanish, the most common nucleus in the most frequent syllables were /a/ and /o/.

```{r apafg-top-syll-freq}
#| label: apafg-top-syll-freq
#| apa-cap: "Top 20 most frequent syllables"
#| fig-width: 8
#| fig-height: 3
#| out-width: 80%
#| echo: false
#| warning: false
#| message: false
syll |> 
    group_by(language) |> 
    top_n(20, freq_syll) |> 
    ggplot(aes(reorder_within(syll, desc(freq_syll), language),
               freq_syll)) +
    facet_wrap(~ language,
               scales = "free_x",
               ncol = 1) +
    geom_col(colour = "white",
             fill = "grey70") +
    labs(x = "Syllable",
         y = "Relative frequency\n(counts per million)",
         colour = "Language",
         fill = "Language") +
    scale_x_reordered() +
    scale_y_continuous(labels = \(x) format(x, big.mark = ",")) +
    theme(legend.position = "none",
          axis.title.x = element_blank(),
          axis.text.x = element_text(size = 10),
          panel.grid = element_blank())
```

@@

We fit this model running `r dim(model_fit_syllables$fit)[2]` sampling chains with `r format(dim(model_fit_syllables$fit)[1], big.mark = ",")` iterations each. {apatb-coefs} shows a summary of the posterior distribution of the fixed effects in the model. As expected, words with more syllables scored higher in syllabic frequency: all posterior draws for the regression coefficient of the main effect of this predictor fell outside the ROPE defined between -0.5 and +0.5 ($\beta$ = `r round(post_draws_list[["b_n_syll_std"]]$.median, 2)`, 95% HDI = [`r round(post_draws_list[["b_n_syll_std"]]$.lower, 2)`, `r round(post_draws_list[["b_n_syll_std"]]$.upper, 2)`]). Keeping the number of syllables constant, the effect of cognateness was negligible: all of the posterior distributions of this predictor fell within the ROPE, providing evidence that the true value of the increment in syllabic frequency for every increase in cognateness is equivalent to zero ($\beta$ = `r round(post_draws_list[["b_lv_std"]]$.median, 2)`, 95% HDI = [`r round(post_draws_list[["b_lv_std"]]$.lower, 2)`, `r round(post_draws_list[["b_lv_std"]]$.upper, 2)`]).

```{r apatb-syllable-coefs}
#| label: apatb-syllable-coefs
#| apa-cap: "Posterior distribution of regression coefficients."
#| apa-note: "Median: median of the posterior distribution in the probability scale. 95\\% HDI: 95\\% highest density interval of the distribution; narrowest range of values that contains 95\\% of the distribution, and therefore is 95\\% likely to contain the true value, given the data. On top of each distribution, we indicate the proportion of posterior samples in the 95\\% HDI that fall into the region of practical equivalence (ROPE). This proportion indicates the probability of the true value of the coefficient being equivalent to zero. Lower values indicate that the true value is unlikely to be zero of equivalent to zero."
#| echo: false
#| message: false
#| warning: false
# summarise posterior draws
post_syllables |> 
    select(.variable_name, .median, .lower, .upper, .rope_overlap) |>
    gt(rowname_col = ".variable_name") |>
    fmt_percent(.rope_overlap, decimals = 2) |> 
    fmt_number(c(.median:.upper), decimals = 2) |>
    cols_merge(c(.lower, .upper),
               pattern = "[{1}, {2}]") |>
    cols_label(
        .variable_name = "Parameter",
        .median = "Median",
        .lower = md("95% HDI"),
        .rope_overlap = md("ROPE prob.")
    ) |>
    tab_style(cell_text(weight = "bold"),
              cells_column_labels(columns = 1:5)) |>
    tab_style(cell_text(align = "left"),
              cells_title(groups = "subtitle")) |> 
    tab_style(cell_text(size = "small"), 
              list(cells_body(),
                   cells_row_groups(),
                   cells_stub())) |> 
    tab_style(cell_text(style = "italic"),
              cells_row_groups())
```

{apafg-syllable-marginal} shows the median posterior-predicted syllabic frequencies for words with one to four syllables, for the whole range of cognateness values. Overall, cognate words' syllabic frequency is equivalent to that of non-cognates. This suggests that the cognate facilitation effect in word acquisition reported in the present study is not the result from an association between cognateness and higher syllabic frequencies.

```{r apafg-syllable-marginal}
#| label: apafg-syllable-marginal
#| apa-cap: "Posterior-predictions of the syllabic frequency model. Thicker lines indicate the median of the posterior predictions, and thinner lines indicate individual posterior predictions."
#| fig-width: 7
#| fig-height: 5
#| out-width: 80%
#| echo: false
#| message: false
#| warning: false
expand_grid(lv_std = scale(seq(0, 1, 0.1),
                           center = mean(syllables_data$lv),
                           scale = sd(syllables_data$lv))[, 1],
            n_syll_std = scale(seq(1, 4, 1),
                               center = mean(syllables_data$n_syll),
                               scale = sd(syllables_data$n_syll))[, 1]) |> 
    add_epred_draws(model_fit_syllables, ndraws = 50,
                    re_formula = NA) |> 
    mutate(lv_std = rescale_variable(lv_std,
                                     mean = mean(syllables_data$lv),
                                     sd = sd(syllables_data$lv)),
           n_syll_std = rescale_variable(n_syll_std,
                                         mean = mean(syllables_data$n_syll),
                                         sd = sd(syllables_data$n_syll)),
           n_syll_std = as.factor(n_syll_std)) |> 
    ggplot(aes(lv_std, .epred, colour = n_syll_std)) +
    geom_point(data = filter(syllables_data, n_syll < 5),
               aes(x = lv,
                   y = freq_syll,
                   colour = as.factor(n_syll)),
               shape = 1,
               stroke = 1,
               alpha = 1/2) +
    geom_line(aes(group = interaction(.draw, n_syll_std)),
              alpha = 1/10) +
    labs(x = "Cognateness (Levenshtein similarity)",
         y = "Syllabic frequency",
         colour = "Number of syllables") +
    scale_color_manual(values = clrs) +
    scale_y_continuous(n.breaks = 8) +
    theme(panel.grid = element_blank())
```

>>>>

```{r tbl-items-table}
#| label: tbl-syll-items
#| tbl-cap: Sample of items included in the BVQ questionnaire and their syllabified SAMPA transcriptions in Catalan and Spanish
#| echo: false
#| warning: false
#| message: false
items |> 
    distinct(te, item, language, meaning, xsampa, n_syll) |> 
    left_join(distinct(pool_tmp, te, language, item, label),
              by = join_by(te, item, language)) |> 
    pivot_wider(names_from = language,
                values_from = c(item, label, xsampa, n_syll),
                id_cols = c(te, meaning),
                names_repair = make_clean_names,
                values_fn = first) |> 
    sample_n(15) |> 
    gt() |> 
    cols_hide(c(te, item_catalan, item_spanish)) |> 
    tab_spanner("Catalan", matches("catalan")) |> 
    tab_spanner("Spanish", matches("spanish")) |> 
    cols_label(meaning = "Translation",
               label_catalan = "Item",
               xsampa_catalan = "X-SAMPA",
               n_syll_catalan = "Syllables",
               label_spanish = "Item",
               xsampa_spanish = "X-SAMPA",
               n_syll_spanish = "Syllables") |> 
    tab_style(cell_text(weight = "bold"),
              cells_column_spanners()) |> 
    tab_style(cell_text(style = "italic"),
              cells_column_labels())
```

Most Catalan and Spanish words had two syllables, with Spanish words having three and four syllables more often than Catalan words. Less than 1% of the words included in the analyses presented in the main body of the manuscripts had five syllables. No words had more than five syllables (see @fig-syll-number). We extracted lexical frequencies from the English corpora in the CHILDES database. Using the Catalan and Spanish corpora was not possible due to the low number of children and tokens included in the corpora.

```{r fig-syll-number}
#| label: fig-syll-number
#| fig-cap: Distribution of the number of syllables in Catalan and Spanish
#| fig-width: 7
#| fig-height: 3
#| echo: false
#| warning: false
#| message: false
pool_tmp |> 
    group_by(language) |> 
    add_count(language, name = "n_lang") |> 
    ungroup() |> 
    count(language, n_lang, n_syll) |> 
    mutate(prop = n/n_lang) |> 
    ggplot(aes(n_syll, n)) +
    facet_wrap(~ language) +
    geom_col(colour = "white", fill = "grey70") +
    geom_text(aes(label = percent(prop)),
              size = 3,
              position = position_nudge(y = 15),
              colour = "black") +
    labs(x = "Number of syllables",
         y = "Number of words",
         fill = "Language") +
    theme(legend.position = "none",
          panel.grid.minor = element_blank(),
          panel.grid.major.x = element_blank())
```

We now present how syllable frequencies were calculated. Every exposure to a word-form also counts as a exposure to each of the syllables that make up such word. Every time a child hears the word *casa* [house], they are exposed to the syllables *ca* and *sa*. Syllables that appear embedded in words with higher lexical frequency will also be more frequent. To compute the relative frequency of each syllable in Catalan and Spanish (i.e., how many times the syllables appears in every million words in Catalan or Spanish speech), we summed the relative lexical frequency in CHILDES of every word that contains such syllable in the corresponding language. @fig-syll-freq shows the distribution of frequencies across syllables in Catalan and Spanish. In the log10 scale, syllable frequencies in Catalan and Spanish followed a slightly asymmetric distribution, with most syllables scoring around 1,000 counts per million, and a longer tail to the right of the distribution.

```{r fig-syll-freq}
#| label: fig-syll-freq
#| fig-cap: "Distribution of apositional syllable frequencies in Spanish and Catalan"
#| fig-height: 3.5
#| fig-width: 7
#| echo: false
#| warning: false
#| message: false
syll <- items |> 
    left_join(distinct(pool_tmp, te, childes_lemma),
              by = join_by(te)) |> 
    left_join(select(childes, token, freq_lex = freq_million),
              by = c("childes_lemma" = "token")) |> 
    select(language, item, te, meaning, xsampa, lv, freq_lex, syll) |> 
    unnest_longer(syll) |> 
    group_by(language, syll) |> 
    summarise(freq_syll = sum(freq_lex),
              .groups = "drop") |> 
    arrange(language, desc(freq_syll))

@@

@fig-top-syll-freq shows the top twenty most frequent syllables in Spanish. In both languages, most of the most frequent syllables followed a consonant-vowel (CV) structured. In Catalan, the most common nucleus in the most frequent syllables was /\textschwa/ (most likely due to vowel reduction in unstressed syllables), followed by /u/. In Spanish, the most common nucleus in the most frequent syllables were /a/ and /o/.

```{r fig-top-syll-freq}
#| label: fig-top-syll-freq
#| fig-cap: "Top 20 most frequent syllables"
#| fig-width: 8
#| fig-height: 3
#| out-width: 80%
#| echo: false
#| warning: false
#| message: false
syll |> 
    group_by(language) |> 
    top_n(20, freq_syll) |> 
    ggplot(aes(reorder_within(syll, desc(freq_syll), language),
               freq_syll)) +
    facet_wrap(~ language,
               scales = "free_x",
               ncol = 1) +
    geom_col(colour = "white",
             fill = "grey70") +
    labs(x = "Syllable",
         y = "Relative frequency\n(counts per million)",
         colour = "Language",
         fill = "Language") +
    scale_x_reordered() +
    scale_y_continuous(labels = \(x) format(x, big.mark = ",")) +
    theme(legend.position = "none",
          axis.title.x = element_blank(),
          axis.text.x = element_text(size = 10),
          panel.grid = element_blank())
```

@@

We fit this model running `r dim(model_fit_syllables$fit)[2]` sampling chains with `r format(dim(model_fit_syllables$fit)[1], big.mark = ",")` iterations each. @tbl-syll-coefs shows a summary of the posterior distribution of the fixed effects in the model. As expected, words with more syllables scored higher in syllabic frequency: all posterior draws for the regression coefficient of the main effect of this predictor fell outside the ROPE defined between -0.5 and +0.5 ($\beta$ = `r round(post_draws_list[["b_n_syll_std"]]$.median, 2)`, 95% HDI = [`r round(post_draws_list[["b_n_syll_std"]]$.lower, 2)`, `r round(post_draws_list[["b_n_syll_std"]]$.upper, 2)`]). Keeping the number of syllables constant, the effect of cognateness was negligible: all of the posterior distributions of this predictor fell within the ROPE, providing evidence that the true value of the increment in syllabic frequency for every increase in cognateness is equivalent to zero ($\beta$ = `r round(post_draws_list[["b_lv_std"]]$.median, 2)`, 95% HDI = [`r round(post_draws_list[["b_lv_std"]]$.lower, 2)`, `r round(post_draws_list[["b_lv_std"]]$.upper, 2)`]).

```{r tbl-syll-coefs}
#| label: tbl-syll-coefs
#| tbl-cap: "Posterior distribution of regression coefficients."
#| tbl-note: "Median: median of the posterior distribution in the probability scale. 95\\% HDI: 95\\% highest density interval of the distribution; narrowest range of values that contains 95\\% of the distribution, and therefore is 95\\% likely to contain the true value, given the data. On top of each distribution, we indicate the proportion of posterior samples in the 95\\% HDI that fall into the region of practical equivalence (ROPE). This proportion indicates the probability of the true value of the coefficient being equivalent to zero. Lower values indicate that the true value is unlikely to be zero of equivalent to zero."
#| echo: false
#| message: false
#| warning: false
# summarise posterior draws
post_syllables |> 
    select(.variable_name, .median, .lower, .upper, .rope_overlap) |>
    gt(rowname_col = ".variable_name") |>
    fmt_percent(.rope_overlap, decimals = 2) |> 
    fmt_number(c(.median:.upper), decimals = 2) |>
    cols_merge(c(.lower, .upper),
               pattern = "[{1}, {2}]") |>
    cols_label(
        .variable_name = "Parameter",
        .median = "Median",
        .lower = md("95% HDI"),
        .rope_overlap = md("ROPE prob.")
    ) |>
    tab_style(cell_text(weight = "bold"),
              cells_column_labels(columns = 1:5)) |>
    tab_style(cell_text(align = "left"),
              cells_title(groups = "subtitle")) |> 
    tab_style(cell_text(size = "small"), 
              list(cells_body(),
                   cells_row_groups(),
                   cells_stub())) |> 
    tab_style(cell_text(style = "italic"),
              cells_row_groups())
```

@tbl-syll-marginal shows the median posterior-predicted syllabic frequencies for words with one to four syllables, for the whole range of cognateness values. Overall, cognate words' syllabic frequency is equivalent to that of non-cognates. This suggests that the cognate facilitation effect in word acquisition reported in the present study is not the result from an association between cognateness and higher syllabic frequencies.

```{r tbl-syll-marginal}
#| label: tbl-syll-marginal
#| tbl-cap: "Posterior-predictions of the syllabic frequency model. Thicker lines indicate the median of the posterior predictions, and thinner lines indicate individual posterior predictions."
#| fig-width: 7
#| fig-height: 5
#| out-width: 80%
#| echo: false
#| message: false
#| warning: false
expand_grid(lv_std = scale(seq(0, 1, 0.1),
                           center = mean(syllables_data$lv),
                           scale = sd(syllables_data$lv))[, 1],
            n_syll_std = scale(seq(1, 4, 1),
                               center = mean(syllables_data$n_syll),
                               scale = sd(syllables_data$n_syll))[, 1]) |> 
    add_epred_draws(model_fit_syllables, ndraws = 50,
                    re_formula = NA) |> 
    mutate(lv_std = rescale_variable(lv_std,
                                     mean = mean(syllables_data$lv),
                                     sd = sd(syllables_data$lv)),
           n_syll_std = rescale_variable(n_syll_std,
                                         mean = mean(syllables_data$n_syll),
                                         sd = sd(syllables_data$n_syll)),
           n_syll_std = as.factor(n_syll_std)) |> 
    ggplot(aes(lv_std, .epred, colour = n_syll_std)) +
    geom_point(data = filter(syllables_data, n_syll < 5),
               aes(x = lv,
                   y = freq_syll,
                   colour = as.factor(n_syll)),
               shape = 1,
               stroke = 1,
               alpha = 1/2) +
    geom_line(aes(group = interaction(.draw, n_syll_std)),
              alpha = 1/10) +
    labs(x = "Cognateness (Levenshtein similarity)",
         y = "Syllabic frequency",
         colour = "Number of syllables") +
    scale_color_manual(values = clrs) +
    scale_y_continuous(n.breaks = 8) +
    theme(panel.grid = element_blank())
```
